Parks Data

### 2019-09-17 02_parks_data.Rmd
Add twitter data to parks data builder

```{r setup}
library(leaflet)
library(tidyverse)
library(RSocrata)
library(leaflet)
library(sf)
```

@@

Now we can join the cemeteries data to the parks data and write out the results
```{r write}
rbind(
  dissolved %>% 
    transmute(id = parknum, name = park_name, acres, courts, playgrounds, trails, 
              type = "park"),
  dissolved_cemeteries %>% 
    transmute(id = source_id, name, acres, courts = FALSE, playgrounds = FALSE, 
              trails = FALSE, type = "cemetery")
  ) %>%
  filter(as.numeric(acres) > 0.5) %>%
  st_simplify(preserveTopology = TRUE) %>%
  write_rds("data/open_spaces.rds") %>%
  geojsonio::geojson_write(file = "data/open_spaces.geojson")
```

>>>>

```{r setup}
library(leaflet)
library(tidyverse)
library(RSocrata)
library(leaflet)
library(sf)
library(lubridate)
```

@@

Now we can join the cemeteries data to the parks data and get a single polygons
layer.
```{r write}
open_spaces <- rbind(
  dissolved %>% 
    transmute(id = parknum, name = park_name, acres, courts, playgrounds, trails, 
              type = "park"),
  dissolved_cemeteries %>% 
    transmute(id = source_id, name, acres, courts = FALSE, playgrounds = FALSE, 
              trails = FALSE, type = "cemetery")
  ) %>%
  filter(as.numeric(acres) > 0.5) %>%
  st_simplify(preserveTopology = TRUE)
```

## Tweet Counts

We obtained geolocated tweets sent from within the boundaries of each park for
the period from July through October, 2014.

```{r tweets}
tweets <- read_csv("data/tweet_counts.csv") %>%
  filter(id %in% open_spaces$id) %>%
  gather(date, count, PK_7_1:PK_10_31) %>%
  separate(date, c("pk", "month", "day"), sep = "_") %>%
  mutate(date = as_date(str_c("2014", month, day, sep = "-"))) %>%
  dplyr::select(id, date, count) %>%
  mutate(
    month = month(date, TRUE),
    wday = wday(date, TRUE)
  ) 
```

We have a question about how consistent the twitter data is by month or across
days of the week. Somewhat surprisingly, the twitter activity is lowest on saturday, 
and then next lowest on Sunday.

```{r wday}
tweets %>%
  ggplot(aes(x = wday)) +
  geom_bar()
```

August is very low! Let's make sure to use September or October.

```{r month}
tweets %>%
  ggplot(aes(x = month)) +
  geom_bar()
```

Let's look at the within-park consistency or variability of twitter activity.
It appears that there is some variation, but that parks with high use typically 
have high use.

```{r consistency}
tweets %>%
  filter(month == "Sep") %>%
  ggplot(aes(x = date, y = count + 1, group = id)) +
  geom_line(alpha = 0.5) + scale_y_log10()
```

Let's calculate the daily average for each park  as well as the total tweets in
September and then go with that.

```{r tweets_summary}
(tweets_summary <- tweets %>%
  filter(month == "Sep") %>%
  filter(!wday %in% c("Sat", "Sun")) %>%
  group_by(id) %>%
  summarise(
    tweet_average = mean(count),
    tweet_count = sum(count)
  ) %>%
  arrange(-tweet_count))
ggplot(tweets_summary, aes(x = tweet_count)) +
  geom_histogram()

open_spaces <- open_spaces %>%
  left_join(tweets_summary, by = "id") %>%
  mutate_at(
    vars(starts_with("tweet")), 
    list(~replace_na(., 0))
  ) 
```

Now we write out the data for the future.
```{r write}
write_rds(open_spaces, "data/open_spaces.rds")
geojsonio::geojson_write(open_spaces, file = "data/open_spaces.geojson")
```
